%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[]{awesome-cv}
\usepackage{textcomp}
%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{blurple}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]
    \begin{document}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Profile
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
	\headerfirstnamestyle{Eashwar}  \headerlastnamestyle{Mohan} \\

	{\color{purple}{\faEnvelope\ \bodyfont{eashwar@umich.edu}}} | {\color{purple}{\faMapMarker\ \bodyfont{San Mateo, CA}}} | {\color{purple}{\faLink\ \bodyfont{eash.dev}}}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-4mm}
\cvsection{Education}
\vspace{-2mm}
\cventry
	{BSE in Computer Science/Minor in Music, Summa Cum Laude}
	{University of Michigan - Ann Arbor}
	{}
	{Sept 2017 - May 2020}
	{\begin{cvitems}
		\item{Degree Completed in 3 Years and Awarded With Highest Honors, GPA: 3.875}
		\end{cvitems}}

\vspace{-5mm}
\cventry
	{MSE in Computer Science}
	{}
	{}
	{Sept 2020 - May 2021}
	{\begin{cvitems}
		\item{GPA: 3.818, Part of Sequential Undergraduate/Graduate Studies program (SUGS)}
		\end{cvitems}}

% \vspace{-4mm}
% \cventry
% 	{High School Dual Enrollment}
% 	{Lansing Community College}
% 	{}
% 	{September 2016-April 2017}
% 	{\begin{cvitems}
% 		\item{GPA: 4.0. Courses Taken: Multivariable Calculus, Linear Algebra}
% 		\end{cvitems}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Employment
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-6mm}
\cvsection{Employment}
\vspace{-2mm}

	
	% \cventry
	% {Graduate Student Instructor, EECS 494: Game Development}
	% {University of Michigan}
	% {Ann Arbor, MI}
	% {August 2020 – Present}
	% {\begin{cvitems}
	% 	\item {Lead weekly discussion sections over auxiliary course material to help students make games in Unity.}
	% 	\item {Manage office hours, a virtual forum board, moderate virtual lecture, and grade assignments.}
	% \end{cvitems}}

	% \vspace{-4mm}
	\cventry
	{Software Engineer, Content Platform}
	{Roblox Corporation}
	{San Mateo, CA}
	{Aug 2021 - Present}
	{\begin{cvitems}
		\item{Working as a backend engineer to support the multi-billion collection of assets which enable the experiences on the platform.}
		\item{Design, implement, and maintain C\#/.NET REST and gRPC APIs and work to decompose an old, monolithic codebase to a microservice architecture.}
		\item{Utilize the Hashicorp suite of tools (Nomad, Consul, Terraform, Vault) as well as Docker to create an effective and agile microservice deployment framework.}
	\end{cvitems}}

	\vspace{-5mm}
	\cventry
	{Software Engineer Intern}
	{}
	{}
	{June 2019 – Aug 2019}
	{\begin{cvitems}
		\item {Designed and implemented a RESTful API in .NET currently receiving thousands of requests a second in production,
		 which keeps track of dependencies between in-game assets on the Roblox game platform.}
		\item {Beta tested a development workflow in Docker Compose, Hashicorp 
		Nomad and Vault, and Drone CI.}
	\end{cvitems}}

	\vspace{-4mm}
	\cventry
	{Software Engineer Intern (2020), Camtasia Team}
	{TechSmith Corporation}
	{Okemos, MI}
	{May 2020 – Aug 2020}
	{\begin{cvitems}
		\item {Enabled Camtasia, the video editor and screen recording program, to work better on mixed-DPI multi-monitor workflows.}
		\item {Localized Camtasia into various non-English languages.}
	\end{cvitems}}

	\vspace{-5mm}
	\cventry
	{Software Engineer Intern (2018), Camtasia Team}
	{}
	{}
	{May 2018 – Aug 2018}
	{\begin{cvitems}
		\item {Mitigated security vulnerabilities related to zip files in Camtasia.}
		\item {Completed various bugfixes and small feature requests.}
		% \item {\textit{(Both internships, worked with MFC and Win32 (C++), and WPF (C\#) technologies)}}
	\end{cvitems}}

	% \vspace{-4mm}
	% \cventry
	% {Technical Lab Assistant}
	% {Crowds and Machines Lab at the University of Michigan}
	% {Ann Arbor, MI}
	% {January 2019 – Present}
	% {\begin{cvitems}
	% 	\item {Educate undergraduate researchers on various tools and skills, such as version control, and software architecture}
	% 	\item {Hold office hours to assist researchers with technical problems and create/maintain documentation for the lab.}
	% \end{cvitems}}

	% \vspace{-4mm}
	% \cventry
	% {Computer Consultant}
	% {University of Michigan Dental Informatics}
	% {Ann Arbor, MI}
	% {September 2017 – May 2019}
	% {\begin{cvitems}
	% 	\item {Assist dental faculty and students of the School of Dentistry over email, phone, and in-person with technological issues}
	% 	\item {File and assign tickets using the ITS and manage the Desktop Support front desk}
	% 	\end{cvitems}}

	% \vspace{-4mm}
	% \cventry
	% {Software Engineer Intern}
	% {Delta Dental of Michigan}
	% {Okemos, MI}
	% {June 2017 – August 2017}
	% {\begin{cvitems}
	% 	\item {Integrated Open ID Connect (OIDC)/SecureAuth with desktop and web applications}
	% 	\item {Designed and implemented a REST API using the Java Persistence API (JPA), and Enterprise JavaBeans (EJB)}
	% 	\end{cvitems}}

\vspace{-6mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Projects}
\vspace{-2mm}

	\cventry
	{Music education puzzle game that teaches the player about drumming and rhythmic intuition. Available on Android and online at projectlegato.com/game/.
	 Made with Unity2D.}
	{GridBeat}
	{GridBeat on Google Play Store}
	{}
	{}

	% \vspace{-6mm}
	% \cventry
	% {A 3D, splitscreen multiplayer spaceship racing game. First place winner of the December 2019 University of Michigan Student Game Showcase.
	%  Made with Unity3D.}
	% {TURBONEON}
	% {deem.itch.io/turboneon}
	% {}
	% {}

	% \vspace{-6mm}
	% \cventry
	% {Control a level of Super Mario Bros. by playing the overworld theme on a MIDI keyboard. Made for MHacks 11.
	%  Made with pygame, pyautogui}
	% {Super MIDIo Bros.}
	% {GitHub: eashwar/super-midio-bros}
	% {}
	% {}

	% \vspace{-6mm}
	% \cventry
	% {Command line tool to control of basic Spotify playback in bash. Made with Express, Bash}
	% {now-playing: Spotify control for Bash}
	% {GitHub: eashwar/now-playing}
	% {}
	% {}
	
	\vspace{-6mm}
	\cventry
	{Songs made using the DAW Reaper, piano, clarinet, and bass clarinet.}
	{Music Composition}
	{eashwar.bandcamp.com}
	{}
	{}
	
	\vspace{-6mm}
	\cventry
	{A personal website displaying a full list of past and current projects. Single-page-app implemented by hand in JavaScript.}
	{Personal Website}
	{eash.dev}
	{}
	{}
	
	\vspace{-5mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Activities
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \newpage
\vspace{-2mm}
\cvsection{Activities}
\vspace{-2mm}
	\cventry
	{Co-Founder and President/Speaker/Bandleader}
	{Video Game Music Club}
	{}
	{January 2018 – Present}
	{\begin{cvitems}
		\item {Lead discussions and workshops on video game music analysis, music theory, composition, and music production}
		\item {Manage mailing lists, online calendar, Discord server, and social media for the club}
		\end{cvitems}}

	\vspace{-4mm}
	\cventry
	{Treasurer (2018-2020) \& Webmaster (2019-2021)}
	{FIRST Alumni and Mentors Network at Michigan (FAMNM)}
	{}
	{Sept 2017 – Present}
	{\begin{cvitems}
		\item {Fundraised over \$25,000 to establish an endowed scholarship for FIRST alumni at the University of Michigan}
		\item {Drafted and submitted funding proposals to facilitate the improvement FAMNM events}
		\item {Maintained the frontend and backend of the club website (https://famnm.club)}
		\end{cvitems}}
	
	\vspace{-4mm}
	\cventry
	{Web Team (2018-19) \& Bootcamp Lead (2019-2020) \& Senior Advisor (2020-2021)}
	{Michigan Hackers}
	{}
	{Jan 2018 – Present}
	{\begin{cvitems}
		\item {Organized weekly presentations to introduce new CS students to concepts essential to academic and career success.}
		\item {Topics include: version control, test-driven development, OOP and FP basics.}
		\item {Developed the front-end and back-end for michiganhackers.org using ReactJS and Gin, a Golang framework.}
		\end{cvitems}}
	\vspace{-4mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Awards
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \vspace{-1mm}
% \cvsection{Awards}
% \vspace{-2mm}
% 	\cventry
% 	{Recipient}
% 	{Leinweber Software Scholarship}
% 	{}
% 	{January 2019 – Present}
% 	{}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \vspace{-3mm}
\cvsection{Skills}
\vspace{-2mm}
	\cventry
	{C++, Java, JavaScript, Python, C\#, Go, XML, XAML, SQL, HTML/CSS, Markdown, LaTeX}
	{Languages}
	{}
	{}
	{}

	\vspace{-8mm}
	\cventry
	{Git, Bash scripting, PowerShell scripting, Windows, OSX, Linux}
	{Tools/OSes}
	{}
	{}
	{}
	
	\vspace{-8mm}
	\cventry
	{Reaper, Ableton, Clarinet (12 years), Piano (16 years), Composition (7 years)}
	{Music}
	{}
	{}
	{}
	\vspace{-4mm}
\end{document}
