%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[]{awesome-cv}
\usepackage{textcomp}
%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{riot-cover-letter/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{green}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]
    \begin{document}

    \begin{flushleft}
        \letterheaderfirstnamestyle{Eashwar} \letterheaderlastnamestyle{Mohan}
    \end{flushleft}

    \begin{flushright}
        \vspace{-10mm}
        {\color{darkgreen}{\faEnvelope\ \bodyfont{eashwar@umich.edu}}}\\
        {\color{darkgreen}{\faMapMarker\ \bodyfont{Ann Arbor, MI}}}\\
    {\color{darkgreen}{\faLink\ \bodyfont{eashwar.github.io}}}
    \end{flushright}

    \recipientname{Riot Games}
    \letterdate{17 September 2018}

    \letteropenclosestyle{To whom it may concern:}

    \descriptionstyle{Hello! My name is Eashwar Mohan, and I'm a student working towards a BSE in computer science and minor in music at the University of Michigan. I'm writing this to express my interest in a software engineering internship at Riot Games for Summer 2019. I became a fan of Riot back in high school when my friends introduced me to League - it was my introduction to the MOBA genre and in my opinion, is the most well-made game in the genre, from the awesome sound design to the continuously rebalancing gameplay.}\\

    \descriptionstyle{In my three semesters so far at the University of Michigan, I've worked towards promoting an environment where people can talk about their love for video games and learn more about it. More specifically, in January 2018 I helped co-found the Video Game Music Club at the University of Michigan - a club devoted to promoting the analysis, composition, and appreciation of video game audio, and to increase interest in the field of game audio as well. I also put my love for games to use in a 2D platforming game of my own that I started developing this summer. It's currently untitled, but is being written in C++ using the SDL2 framework and Catch2 for unit testing. I feel that the passion I have for making and sharing games gives me a unique perspective that I could bring to an internship at Riot.}\\

    \descriptionstyle{Looking at the Riot Games website, one of the internship opportunities that interests me the most is that of writing “cross-platform code to power native applications on disparate mobile devices in order to allow players to connect with each other from anywhere on the planet”. In this past summer of 2018, I had an internship at TechSmith Corporation in Okemos, Michigan. There, I worked on a native Windows application for video editing called Camtasia, which also happens to have an OSX edition. While I spent the former half working with Microsoft’s WPF to improve the product, the work I enjoyed the most was working on the shared code that both Camtasia's Mac and Windows ports utilized for rendering and screen capture. I would love the opportunity to work on cross-platform code to help bring people together.}\\

    \descriptionstyle{In terms of my favorite gaming experience, one memory sticks out in particular - beating the story mode of Super Smash Bros. Brawl for the first time with my sister and cousin. The “Subspace Emissary” campaign mode featured a long plot involving all of Nintendo's heroes and villains battling as the multiverse was on the verge of collapse, due to the god-like being “Tabuu”. The boss fight with Tabuu was the hardest boss fight in my childhood, with many randomized, nearly undodgeable attacks, and the satisfaction that I felt when we dealt the final blow (with Sonic the Hedgehog, of course) continues to be unexplainable to me. Since then, many boss fights have gotten very close to giving me that same feeling, but I still am searching for something that can actually top it.}\\

    \descriptionstyle{I would really value an internship at Riot Games. It would be an incredible experience and I truly believe that my experience can be put to great use there.}
    \\

    \letteropenclosestyle{Regards,}\\

    \letteropenclosestyle{Eashwar Mohan}

\end{document}